---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/tmbr.svg?branch=master)](https://travis-ci.org/poissonconsulting/tmbr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/tmbr?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/tmbr)
[![codecov](https://codecov.io/gh/poissonconsulting/tmbr/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/tmbr)

# tmbr

## Introduction

`tmbr` (pronounced timber) is an R package to facilitate analyses using Template Model Builder (TMB).

## Demonstration

```{r}
library(tmbr)

model_code <- "
#include <TMB.hpp>

template<class Type>
Type objective_function<Type>::operator() () {
DATA_VECTOR(wt);
DATA_VECTOR(hp);
DATA_VECTOR(disp);
DATA_VECTOR(mpg);

PARAMETER(bIntercept); 
PARAMETER(bWt); 
PARAMETER(bHp); 
PARAMETER(bDisp); 
PARAMETER(log_sigma);

Type sigma = exp(log_sigma);

int n = wt.size();

Type nll = 0.0;
for(int i = 0; i < n; i++){
  nll -= dnorm(mpg[i], bIntercept + bWt * wt[i] + bHp * hp[i] + bDisp * disp[i], sigma, true);
}

return nll;
}"

gen_inits <- function(data) list(bIntercept = 0, bWt = 0, bHp = 0, bDisp = 0, log_sigma = 0)

model <- tmb_model(model_code, gen_inits = gen_inits, scale = c("wt", "hp", "disp"))

analysis <- analyse(model, data = mtcars)

coef(analysis)
logLik(analysis)

analysis2 <- lm(mpg ~ wt + hp + disp, 
        data = rescale::rescale(mtcars, scale = c("wt", "hp", "disp")))

summary(analysis2)
logLik(analysis)
```

## Installation

To install from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/tmbr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/tmbr/issues).

[Pull requests](https://github.com/poissonconsulting/tmbr/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## Inspiration

- [jaggernaut](https://github.com/poissonconsulting/jaggernaut)

## Documentation

- [TMB](https://github.com/kaskr/adcomp)
